Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-08 tensor/draft/draft-tensor-op.tex
[tensor/draft] update all plots with identical colors
* replace Christoph's last figure
* rerun SM unc. predictions with new KDE contour computation and smaller
  range in cT

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
  provides a lepton-forward-backward asymmetry, $A_{\rm FB}^\ell$, and a flat
  term, $F_H^\ell$, that are strongly suppressed in the standard model. In both,
  nonstandard tensor and scalar contributions are enhanced with respect
  to vector ones. We use latest experimental results for $\ell = \mu$ in
  combination with $B_s\to \bar\mu\mu$ to derive stronger model-independent
  constraints on tensor and scalar effective couplings and determine their
  impact on not yet measured angular observables in
  $B\to K^*\bar\mu\mu$, which feature the same suppression of vector couplings.
  Most notably, the measurement of $F_H^\mu$ provides
  constraints on (pseudo-)scalar couplings and their chirality-flipped
  counterparts that are complementary to the ones from the branching ratio
  $B_s\to \bar\mu\mu$, which allows to put for the first time simultaneously
  upper bounds on all four couplings.
\end{abstract}

@@

\begin{figure*}
  \includegraphics[width=.35\textwidth]{plots/pdf/res-real_SSp_constr.pdf}
  \includegraphics[width=.35\textwidth]{plots/pdf/res-cmplx_SSp_constr.pdf}
  \caption{
    \eos{
    Constraints on real-valued [left] and complex-valued [right] scalar couplings
    $\wilson{S,\,S'}$ in the scenario SM-EFT from only $\overline{\cal B}(B_s \to
    \bar\mu\mu)$ (blue) and all data in \reftab{tab:observables} (green)
    at 68\% (darker) and 95\% (lighter) probability when marginalising
    over non-zero $\mbox{Re}(\wilson[NP]{10}) \in [-1,\, 9]$ as well as and
    $\mbox{Im}(\wilson[NP]{10})$ and $\mbox{Re, Im}(\wilson[NP]{10'}) \in [-5,\,5]$.
    For comparison the according constraints from all data when keeping
    $\mbox{Re, Im}(\wilson[NP]{10,\, 10'}) = 0$ (red)
    at 68\% (darker) and 95\% (lighter) probability.
    }
  }
  \label{fig:scalar:SM-EFT}
\end{figure*}

>>>>

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell =
  e,\,\mu,\,\tau$) provides a lepton-forward-backward asymmetry,
  $A_{\rm FB}^\ell$, and a flat term, $F_H^\ell$, that are strongly
  suppressed in the standard model. In both, nonstandard tensor and
  scalar contributions are enhanced with respect to vector ones. We
  use latest experimental results for $\ell = \mu$ in combination with
  $B_s\to \bar\mu\mu$ to derive stronger model-independent constraints
  on tensor and scalar effective couplings and determine their impact
  on not yet measured angular observables in $B\to K^*\bar\mu\mu$,
  which feature the same suppression of vector couplings.  Most
  notably, the measurement of $F_H^\mu$ provides constraints on
  (pseudo-)scalar couplings and their chirality-flipped counterparts
  that are complementary to the ones from the branching ratio $B_s\to
  \bar\mu\mu$, which allows to put for the first time simultaneously
  upper bounds on all four couplings. \fred{Try to shorten, add
    sentence ``independent of deviations in vector-coupling dominated
    observables''}
\end{abstract}

@@

\begin{figure*}
  \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_0,2}
  \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_1,3}
  \caption{
    \eos{
    Constraints on real-valued [left] and complex-valued [right] scalar couplings
    $\wilson{S,\,S'}$ in the scenario SM-EFT from only $\overline{\cal B}(B_s \to
    \bar\mu\mu)$ (blue) and all data in \reftab{tab:observables} (green)
    at 68\% (darker) and 95\% (lighter) probability when marginalising
    over non-zero $\mbox{Re}(\wilson[NP]{10}) \in [-1,\, 9]$ as well as and
    $\mbox{Im}(\wilson[NP]{10})$ and $\mbox{Re, Im}(\wilson[NP]{10'}) \in [-5,\,5]$.
    For comparison the according constraints from all data when keeping
    $\mbox{Re, Im}(\wilson[NP]{10,\, 10'}) = 0$ (red)
    at 68\% (darker) and 95\% (lighter) probability.
    }
  }
  \label{fig:scalar:SM-EFT}
\end{figure*}
